% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"


\documentclass{resume}
\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{linespacing_fix} % disable extra space before next section
\usepackage{cite}
\usepackage{comment}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Xinyu Chen}
\contactInfo{https://github.com/cxy7988}


\section{Education}
\datedsubsection{\textbf{Wenzhou-Kean University, CN}}{Sep. 2022–Now}
\datedsubsection{\qquad Exchange in \textbf{Kean University, US}}{Aug. 2024-Mar. 2025}
\textbf{GPA} 3.86/4 (major GPA: 3.96)
\\ \textbf{B.S.} in Management(Business Analytic),\textbf{ minor} in Computer Science
\\ \textbf{Courses:} Java Programming(A), Operating System(A), Database(A), AR Development(A), Data Structure

\hspace{1.5cm} Linear Algebra(A), Statistic(A), Discrete Mathematics, Calculus
 


\section{Work Experience}
%切记！！！！如果CS和DS申一个项目，时间要对齐！！！！！！！！1
\datedsubsection{\textbf{Wenzhou-Kean University}, Peer Tutor}{Oct. 2025-Now}
\begin{itemize}
  \item Served as a peer tutor for Java and Python programming courses, and also taught courses such as Computer Operating Systems and Data Mining.
\end{itemize}


\datedsubsection{\textbf{Proya Cosmetics Co., Ltd.},  Data Analyst}{Aug. 2025}
\begin{itemize}
  \item Obtain business data from data platforms such as Alibaba and ByteDance, and conduct data preprocessing, including data cleaning and data annotation.
  \item Monitor the updates and comments of KOLs on social platforms such as Weibo and Xiaohongshu, and conduct natural language analysis based on the existing dictionaries.
\end{itemize}

\datedsubsection{\textbf{Firstack Limited Liability Company}, Software Design Engineer}{Jun. 2025–Aug. 2025}
\begin{itemize}
  \item Engineered an oscilloscope software with \textbf{Qt}, streamlining hardware debugging and enabling real-time waveform visualization, cutting hardware‑debug time per iteration from 15 min to 5 min.
  \item Refactored \textbf{C/C++} legacy codebase by applying MVC design, redesigning data models and rendering widgets, and optimizing filtering logic for large datasets—resulting in a 20\% performance gain.
\end{itemize}

\datedsubsection{\textbf{Firstack Limited Liability Company}, Financial Data Assitant}{Jun. 2023–Aug. 2023}
\begin{itemize}
  \item Optimized financial data workflows by integrating \textbf{SQL} to overcome Excel performance limitations, enabling efficient cleaning and validation of datasets—including \$100M in fixed assets.
  \item Conducted data analysis on 200+ financial documents to ensure CSRC IPO compliance, helping shorten IPO reporting cycle by 2 weeks
\end{itemize}

\datedsubsection{\textbf{Zhejiang University Research Project}, Data Analyst}{Jul. 2022–Aug. 2022}
\begin{itemize}
  \item Interviewed 100+ rural families and used Excel to organize and visualize survey data through charts and pivot tables, supporting socioeconomic analysis for rural development research.
  \item Co-authored the research report with professors and proposed improvement for province government agencies.
\end{itemize}


\section{Projects and Activities}
\datedsubsection{\textbf{Campus Card \& Utility Fee Query App}}{Jun. 2025-Now}
\begin{itemize}
  \item Reverse-engineered OAuth2 flow using \textbf{Fiddler} and decrypted AES payload to reconstruct undocumented \textbf{REST} APIs for campus card and utility data access.
  \item Built \textbf{Flask} backend with RESTful API and \textbf{SQLite} database to store daily usage records and automate APNs push notifications for balance and utility alerts.
  \item Developed iOS frontend in \textbf{Swift} with async fetching, dynamic UI, and secure email login%app deployed in school with over 100 active users.
\end{itemize}

\datedsubsection{\textbf{Official Course Table Conversion Software}}{Oct. 2025}
\begin{itemize}
  \item Built a Python application that extracts course schedule data from PDF documents using pdfplumber and tabula-py, with intelligent parsing to handle multiple table formats and clean messy data
  \item Developed an end-to-end pipeline converting PDF data to structured CSV and ICS calendar formats, with smart fallback logic and interactive CLI for seamless user experience
  \item Designed modular classes for course data modeling using pandas, implemented clean separation of concerns with robust error handling and multi-format output support
\end{itemize}

\datedsubsection{\textbf{Kaggle Competition - Predict the Introverts from the Extroverts}}{Jul. 2025}
\begin{itemize}
  \item Built a three-stage Stacking framework combining \textbf{neural network} feature extraction with traditional algorithms like \textbf{Random Forest} and \textbf{XGBoost}, achieving multi-model ensemble prediction
  \item Applied IterativeImputer for missing values and \textbf{SMOTE} for class imbalance, optimized hyperparameters via GridSearchCV with cross-validation, achieved 97.17\% validation accuracy
  \item Delivered complete pipeline from data exploration and feature engineering to model deployment, implemented AUC-weighted ensemble strategy with multiple prediction versions
\end{itemize}

% 重复了应该不用写了% \datedsubsection{\textbf{Oscilloscope Software with Communication and Data Filtering}}{June 2025-July 2025}
% \begin{itemize}
%   \item Developed a feature-rich oscilloscope application with real-time serial data communication and advanced digital filtering capabilities by \textbf{C++}, handling datasets of up to over 3000 KB/s. 
%   \item Designed the frontend framework in \textbf{Qt}, leveraging Qt Designer for efficient UI layout and integrating \textbf{JSON}-driven dynamic UI generation for customizable user experiences.
%   \item Applied MVC principles to decouple data management from presentation, enabling efficient data filtering and scalable TableView rendering for large datasets with minimal performance overhead(saving 20\%).
% \end{itemize}

\datedsubsection{\textbf{Virtual Reality Shopping Display System for Pop-up Stores}}{Apr. 2025-May. 2025}
\begin{itemize}
  \item Built AR shopping system in \textbf{Unity} enabling users to scan physical labels and interact with 3D product models, reducing physical sample costs and improving demo efficiency at pop-up stores.
  \item Optimized animation rendering and user event triggers by \textbf{C\#}, implementing dynamic button controls and reducing interaction latency by 35\%.
\end{itemize}

\datedsubsection{\textbf{xv6 Operating System Optimization}}{Feb. 2025-May. 2025}
\begin{itemize}
  \item Implemented a user-level shutdown system call in xv6 using low-level I/O port instructions, reducing manual test overhead
  \item Designed and built a Multi-Level Feedback Queue scheduler with dynamic priority adjustment and aging policy, improving multitasking responsiveness and fairness by 60\%.
  \item Developed a Lazy Page Allocator for on-demand physical page allocation, reducing unused memory footprint and increasing overall memory efficiency 20\%.
\end{itemize}

% 申研简历里不要写进去，因为没发表
\datedsubsection{\textbf{Finance Research}, \textit{Do Repurchase increase the output of Innovation}}{Sep. 2023-May. 2024}
\begin{itemize}
  \item Developed automated Python web crawlers and utilized \textbf{SQL} for large-scale data collection, cleaning, and integration, reducing data preparation time from weeks to days.
  \item Built regression and PSM-DID models in \textbf{Stata} with high explanatory power (avg R² = 0.91), achieving statistically significant results (p < 0.01) across 100K+ firms.
  \item Discovered a significant positive relationship between share repurchases and patent output; co-authored a paper accepted for presentation at the Multinational Finance Society Conference (Finland, 2024).
\end{itemize}

\datedsubsection{\textbf{KPMG ESG Case Study Competition}, Qualify for the final}{Oct. 2023}
\begin{itemize}
  \item Led a 4-member team to design ESG strategies for Ant Group's rural finance expansion; directed data analysis and presentation efforts that helped qualify for the national finals.
  \item Processed and analyzed loan data from 10,000+ households in 100+ rural regions using \textbf{Snowflake}, and created interactive \textbf{Tableau} dashboards to present actionable insights in the final report.
  \item Built regression and k-means models in \textbf{KNIME} to assess the impact of ESG behaviors on loan profitability—helping reduce bad debt rate by 0.3\% and narrow wealth gap index by 0.2\%.
\end{itemize}

\section{Rewards}
\textbf{International Study Scholarship} -  First Prize (Top10 in University)\hfill{Jan. 2025}

\textbf{WKU College Scholarship} - Third Prize (Top5 in Major)\hfill{Nov. 2024}

\textbf{WorldQuant Quantitative Trading Challenge} - Bronze Prize\hfill{May. 2024}

\textbf{Bloomberg Stock Challenge} - No.139 in Asia\hfill{Dec. 2023}

\textbf{The 14th College Students' Career Planning Competition} - Third Prize\hfill{Nov. 2022}



\end{document}


\end{document}
